---
title: "Developing Data Products  Week2"
author: "Andreia Vieira"
date: "07/07/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
```
## SUMMARY 

###### This activity create a web page using R Markdown and  features a map created with Leaflet. The dataset show the MONITORING PANEL COVID-19 in neighborhoods of Manaus/AM,  in start july Brazil, cases  / 100.000 hab. The dataset  of population of the censo 2010 

##  DATA 

###### COVID-19 Manaus/AM - incidence: cases by 100. 000 hab. in 02 July  2020
<font size ="2"> Fundação de vigilância sanitária – FVS/AM 
Download http://www.fvs.am.gov.br/indicadorSalaSituacao_view/60/2 </font>


###### Population and households - Censo 2010 Manaus/AM
<font size ="2"> IBGE
Download ftp://ftp.ibge.gov.br/Censos/Censo_Demografico_2010/Resultados_do_Universo/Agregados_por_Setores_Censitarios/AM_20171016.zip </font>


```{r, warning=FALSE, message=FALSE}


library(leaflet)
library(dplyr)
library(htmltools)

# Leitura dos dados
covid<-setwd("C:/Mana/ACursoCienciadeDados/Aulas/Desenvolvendo Dados/Projetos")
covid<-read.csv("./COVID2019.csv", header=TRUE, sep=";")


```
## DATASET
```{r, warning=FALSE, echo=TRUE}

head(covid)

```

```{r}

#Grupos
covid <- covid %>%
dplyr::mutate(grupo = cut(TAXACOVID, breaks = c(0, 500, 1000, 2000, Inf), labels = c("Abaixo de 500", "Entre 500 e 1000", "Entre 1000 e 2000", "Acima de 2000"))) 


pal <- colorNumeric(
  palette = "YlOrRd",
  domain = covid$POPULACAO,
)

# Verificiar incidência da doença
leaflet() %>%
addTiles() %>%
addCircleMarkers(data=covid, lat = ~LATITUDE, lng =~LONGITUDE, 
                 radius = ~sqrt(covid$POPULACAO/1000),
color=~pal(covid$POPULACAO),
popup = ~htmltools::htmlEscape(covid$POPULACAO),
stroke = FALSE, fillOpacity = 1)->map1


map1%>% addLegend("topright", pal=pal ,  values = covid$POPULACAO,title ='POPULATION CENSO 2010 <br /> <center> NEIGHBORHOODS <br/>  MANAUS/AM  ', opacity = 1) -> map2


pal2<-colorFactor(c("#ffce00","#ff9a00","#EE4540","#933b27"), domain = covid$grupo, reverse = FALSE)
                    
                    
pal3<- colorFactor(c("#E7305B"), domain = covid$POPULACAO, ordered = FALSE)
  
leaflet()%>%
addTiles() %>%
addCircleMarkers(data=covid,
                 lat = ~LATITUDE, 
                 lng = ~LONGITUDE, 
                 radius = ~sqrt(covid$POPULACAO/1000),
                 color = ~pal2(covid$grupo),                
                 popup = ~htmltools::htmlEscape(covid$grupo),
                 stroke = FALSE, fillOpacity = 1)->map3

map3%>% addLegend("topright", pal = pal2 ,  values = covid$grupo,title = '<center> COVID19 - MANAUS/AM <br /> <center>  cases /100.000 hab <br> 02/07/2020 <br/> <font size="0.5" </font>* Larger circle, larger population;<br/> smaller circle, smaller population', opacity = 1) -> map4



```
##  POPULATION NEIGHBORHOODS MANAUS/AM 

```{r, warnings=FALSE, eval=TRUE}
  
browsable(
  tagList(list(
    tags$head(
      tags$style(
        ".leaflet .legend {
                 line-height: 20px;
                 font-size: 12px;
                 }",
        ".leaflet .legend i{
        
            border-radius: 50%;
            width:15px;
            height: 15px;
            margin-top: 2px;
        } "
       )
     ),
   map2
  ))
)
  
```

##  <font size="12">COVID19 - MANAUS/AM </font>

```{r}
library(htmltools)
browsable(
  tagList(list(
    tags$head(
      tags$style(
        ".leaflet .legend {
                 line-height: 20px;
                 font-size: 12px;
                 }",
        ".leaflet .legend i{
        
            border-radius: 50%;
            width:15px;
            height: 15px;
            margin-top: 2px;
        } "
       )
     ),
   map4
  ))
)

```

## <font size="12"> CONSIDERATIONS </font>

- Most neighborhoods have more than 500 cases by 100.000 hab.

- Highlight for less populated neighborhoods with very high rates





